---
title: "The linmod package"
subtitle: "A first course in LM using the present package."
author: "Thomas Kiefer"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    df_print: paged
    number_sections: yes
    toc: no
    toc_depth: 2
  html_document:
    number_sections: yes
    toc: no
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{First course in LM using the linmod package}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
csl: "apa6.csl"
bibliography: "references.bib"
link-citations: yes
lang: de
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. 
Because they are part of the distribution of the package, they need to be as 
compact as possible. 
The `html_vignette` output type provides a custom style sheet (and tweaks some 
options) to ensure that the resulting html is as small as possible. 
The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block 
above. 
These are required in order to instruct R how to build the vignette. 
Note that you should change the `title` field and the `\VignetteIndexEntry` to 
match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. 
To override this theme you can specify your own CSS in the document metadata 
as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images 
side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in 
**knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, 
footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))

## Include

Das einzige was ich hier noch hinzufügen möchte, ist die Möglichkeit 
im APA-Stil zu zitieren. 
Zum Beispiel @RCore2022, oder in einer Klammer [@RCore2022].

# Literaturverzeichnis
